Twists of supersymmetric gauge theories

### 2019-08-14 paper.tex
Continuing edits to SYM section, and to dimensional reduction section

\subsubsection{Yang-Mills Theory}
Let us now give an example of a theory which is not partially holomorphic.  We will give a general description of Yang-Mills theory on $\RR^n$, with spinorial matter.  Fix a complex semisimple Lie group $G$ with Lie algebra $\fg$, and a spinorial representation $\Sigma$ of $\so(n;\CC)$ with symmetric equivariant pairing $\Gamma \colon \Sigma \otimes \Sigma \to \CC^n$.  The ordinary fields of super Yang-Mills theory on $\RR^{n}$ consist of:
\begin{itemize}
\item A connection $A \in \Omega^1(\RR^{n} ; \fg)$ on the trivial $G$-bundle;
\item A $\gg$-valued section $\lambda \in \Omega^0(\RR^{n}) \otimes \Pi \Sigma \otimes \fg$ of the spinor bundle associated to the representation $\Sigma$
\footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of a real spinor bundle, whose structure is signature dependent.  For our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.}.  
\end{itemize}
These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{n}$. 
Hence, there is a single ghost for the theory given by a $\gg$-valued section of the trivial $G$-bundle $c \in \Omega^0(\RR^{n} ; \fg)$.

@@

\begin{prop} \label{dim_red_SUSY_prop}
The dimensional reduction of a supersymmetric classical field theory on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
\end{prop}

\begin{proof}
 \chris{I think this will be straightforward.}
\end{proof}

@@

We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
\begin{enumerate}
 \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ \chris{define this above}, which is only well-defined on-shell.  In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
 \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
\end{enumerate}
This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.  In particular, we will use the following ``3-$\psi$'s rule'' \chris{see citations in Baez Huerta for more references, which we might include}.  Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.

@@

\begin{proof}
\chris{todo:rewrite}
Both are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.  Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, (as in \cite{Guillen}):
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

@@

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where \chris{sign}
\begin{align*}
I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & = \pm \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

@@

\begin{proof}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed \chris{...}
\end{proof}

@@

\begin{proof}
First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since 
\chris{...}
\end{proof}

@@

First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.  Baez and Huerta prove that in our four critical dimensions \chris{argue why this is the same}.

@@

\chris{Discuss dimensional reduction, and then the inclusion of the action of R-symmetries.}

>>>>

\subsubsection{Yang-Mills Theory} \label{YM_section}
Let us now give an example of a theory which is not partially holomorphic.  We will give a general description of Yang-Mills theory on $\RR^n$, with spinorial matter.  Fix a complex semisimple Lie group $G$ with Lie algebra $\fg$, and a spinorial representation $\Sigma$ of $\so(n;\CC)$ with symmetric equivariant pairing $\Gamma \colon \Sigma \otimes \Sigma \to \CC^n$.  The ordinary fields of super Yang-Mills theory on $\RR^{n}$ consist of:
\begin{itemize}
\item A connection $A \in \Omega^1(\RR^{n} ; \fg)$ on the trivial $G$-bundle;
\item A $\gg$-valued section $\lambda \in \Omega^0(\RR^{n}) \otimes \Pi \Sigma \otimes \fg$ of the spinor bundle associated to the representation $\Sigma$
\footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of a real spinor bundle, whose structure is signature dependent.  For our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.}.  
\end{itemize}
These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{n}$. 
Hence, there is a single ghost for the theory given by a $\gg$-valued section of the trivial $G$-bundle $c \in \Omega^0(\RR^{n} ; \fg)$.

@@

\begin{prop} \label{dim_red_SUSY_prop}
The dimensional reduction of a supersymmetric classical field theory $\mf L$ on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory $\mf L'$ on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
\end{prop}

\begin{proof}
 \chris{Proof idea: start with an equivariant action functional $\mf S$ in $n$-dimensions.  There is a cochain map $C^\bullet_{\mr{loc}}(\mf L) \to C^\bullet_{\mr{loc}}(\mf L')$ by restriction.  There is a graded linear map $C^\bullet_{\mr{Lie}(\mf A) \to C^\bullet_{\mr{Lie}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.  However these two maps do, together, define a cochain map
 \[F \colon (C^\bullet_{\mr{Lie}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))_{\mr{Poin}} \to (C^\bullet_{\mr{Lie}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))_{\mr{Poin}},\]
 on the subcomplex consisting of those functionals where, upon restriction

 We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S) = \mf S'$ in $m$-dimensions, i.e a supersymmetric action functional.
 }
\end{proof}

@@

We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
\begin{enumerate}
 \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ as discussed in Section \ref{YM_section}, which is only well-defined on-shell.  In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion.
 \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
\end{enumerate}
This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.  In particular, we will use the following ``3-$\psi$'s rule'', discussed in the 10-dimensional case by Schray \cite{Schray} .  Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.

@@

\begin{proof}
\chris{I'm leaving this for now, but Pavel wanted to rewrite this coordinate freely.}
Both are direct calculations using standard Clifford relations which cite below.
So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.  Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, (as in \cite{Guillen}):
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
\end{align*}
using the fact that 
\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
\end{align*}
\end{proof}

@@

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where \chris{correct sign?}
\begin{align*}
I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & = - \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

@@

\begin{proof}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ is exactly  \chris{...}
\end{proof}

@@

\begin{proof}
First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since the Lie bracket between a supertranslation and an ordinary translation is always zero.  If we then consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
\chris{...}
\end{proof}

@@

First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.  Baez and Huerta prove that in our four critical dimensions, the variation $\delta^{(1)}S_{\mr{BRST}}$ of the ordinary BRST action functional vanishes.  In particular, this implies that $\delta^{(1)}S_{\mr{BV}} = \{I^{(1)}, S_{\mr{BV}}\}$ also vanishes, since \chris{why?}.

@@

We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
\begin{corollary}
Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.  Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.  Then the super Poincar\'e algebra
\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
\end{corollary}

\begin{proof}
This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
\end{proof}

\begin{remark}
We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
\end{remark}
